A Topic Model of Climate Change Literature

### 2018-07-13 main.tex

%\multicollinenumbers

The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}. This role is vital....

Various researchers have attempted to analyse the IPCC's assessment reports \citep{jabbour2017}, criticised the assessment processes of the IPCC. \citep{Bjurström2011} ref ref. Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\linewidth]{plots/volume_variety.png}
		%\captionof{figure}
		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents the average word occurs in is given in the key.
		}
		\label{growth}
	\end{center}
\end{figure}

Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature. Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.

@@

Indeed, this same problem of scale makes attempts to criticise the IPCC as assessment-makers more difficult. These too can be strengthened by big literature approaches. + examples.
%Indeed this same approach is required if researchers are to make convincing claims about what areas of the literature are well-covered, and what are overlooked.

This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large set of literature. This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.

@@

\begin{figure}
\begin{center}
	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
    \caption{}
    \label{}
    \end{center}
\end{figure}

Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},

@@

\subsection*{Data}
This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of

>>>>

%\multicollinenumbers
\bigskip
\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC makes maps.}

The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}. This role is vital for....
Making maps \citep{Edenhofer2015}

\bigskip
\noindent\textbf{The task of the IPCC has beome much more difficult with big literature}

Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}. 
Is the map up to date, does it cover everything?

%%%%%

\bigskip
\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered problems of scale though}

Various researchers have attempted to do empirical research on the assessment reports, and processes of the inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011}. Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}

\bigskip
\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}

Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}

Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}

\bigskip
\noindent\textbf{The scale of the problem in context}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
		%\captionof{figure}
		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
		}
		\label{growth}
	\end{center}
\end{figure}

\bigskip
\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}

Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature. Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments. Similarly, it becomes harder to criticise, with quantitavely evidenced claims, the outcomes of assessment processes.

\bigskip
\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, unmanageably large datasets}

\citep{Greene2016} \citep{Lee1999}

This reduced form description makes comparisons more useful, when cutting the dataset.

\bigskip
\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}

@@

\bigskip
\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}

This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large set of literature. This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it. In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
		\label{}
	\end{center}
\end{figure}

\bigskip
\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}

(partly: Model less good at describing literature later on)

\bigskip
\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}

\bigskip
\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}

(compare to biochar, which is much more recent)

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
		\caption{}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
		\caption{SI}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
    \caption{SI}
    \label{}
    \end{center}
\end{figure}

\bigskip
\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}

\bigskip
\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}

\bigskip
\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}

Negative emissions in special report on 1.5, demand side chapter in AR6

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
		\caption{}
		\label{}
	\end{center}
\end{figure}

\section*{Discussion}

\bigskip
\noindent\textbf{Solutions, policies and science}

%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},

@@

\subsection*{Data}
%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
